---
title: "viz_and_eda"
author: "Shelley Shen"
date: "10/6/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## Scatterplots!

Create my first scatterplot ever

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

New approach, same plot.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Save and edit a plot object.

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```


## Advanced scatterplot...

Start with the same one and make it fancy!
Makes smooth line trajectory when aes defined in original ggplot 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) +
  geom_smooth()
```

Let's facet some things!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, alpha = tmin, color = name)) + 
  geom_point() +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

Let's combine some elements and try a new plot.

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```
facet_grid --> gradient of transparency
geom_point(aes(size = prcp)) --> creates varied sizes depending on prcp



## Some small notes

How many geoms have to exist?

You can have whatever geoms you want. 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```














